### 2016-03-16 Projects/DelCo_2014_2015/Reports/FDS_Validation_Report/TeX_Files/FDS_Exp_Description_Report.tex
Added channel lists to gas burner exp report

\subsection{Layout}
\label{sec:layout}
Dimensioned floor plans of the east and West Structures are presented in Figures~\ref{fig:east_dimensioned_plan}~and~\ref{fig:west_dimensioned_plan}, respectively.

@@

\begin{figure}[!ht]
	\includegraphics[width=\columnwidth]{..//Figures/Floor_Plans/West_Structure_2nd_Floor_Dimensioned_Full}
	\\~\\
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/West_Structure_1st_Floor_Dimensioned_Full}
	\caption[Dimensioned floor plans of the West Structure.]{Dimensioned floor plan of the second floor (top) and first floor (bottom) of the West Structure.}
	\label{fig:west_dimensioned_plan}
\end{figure}

The interior dimensions of each structure were approximately 6.1~m (20~ft) wide, 11~m (36~ft) long, and 2.4~m (8~ft) high. The stairs connecting the two floors of the West Structure started 1.6~m (5.25~ft) off the south wall with a width of 1.2~m (4~ft) off the east wall. The exterior doors of both structures, the stairwell door on the second level of the West Structure, and a square roof vent with side length 1.2~m (4~ft) were opened and closed at certain instances during experiments to change the ventilation patterns within the structures.
\FloatBarrier

@@

\subsubsection{East Structure}
The East Structure was instrumented with five bare-bead thermocouple arrays, four bi-directional probe plus solid thermocouple arrays, five total heat flux plus radiometer sensor pairs, and two gas sample inlet pipes at the locations shown in Fig.~\ref{fig:east_instrumentation}.

\begin{figure}[!ht]
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/East_Structure_Dimensioned_Instrumentation}
	\caption{Location of instrumentation in the East Structure.}
	\label{fig:east_instrumentation}
\end{figure}

Each bare-bead thermocouple array was composed of eight thermocouples. The top sensor was 0.03~m (1~in) below the ceiling and the remaining thermocouples were spaced 0.3~m (1~ft) apart with the bottom thermocouple being 2.13~m (7~ft) below the ceiling. Three bi-directional probe and solid thermocouple arrays, centered in each exterior doorway of the structure, contained eight probes with the first probe 0.08~m (0.25~ft) below the soffit and the remaining probes at 0.34~m (1.1~ft), 0.61~m (2~ft), 0.88~m (2.9~ft), 1.15~m (3.7~ft), 1.42~m (4.7~ft), 1.68~m (5.5~ft), and 1.95~m (6.4~ft) below the soffit as shown in Fig.~\ref{fig:BDP_arrays}. The fourth bi-directional probe plus solid thermocouple array was located at opening of the roof vent and contained three probes located approximately 0.30~m (1~ft), 0.61~m (2~ft), and 0.91~m (3~ft) off the north wall of the vent and centered between the east and west sides of the vent as pictured in Fig.~\ref{fig:BDP_arrays}. The total heat flux guage/radiometer pairs were set to be 0.15~m (0.5~ft) off the ground and aimed to view the ceiling. Gas concentrations were pulled through 9.5~mm (0.375~in) diameter stainless steel tubing located 1.2~m (4~ft) above the floor.

@@

\FloatBarrier

\subsubsection{West Structure}
The first floor of the West Structure was instrumented with three bare-bead thermocouple arrays, three bi-directional probe plus solid thermocouple arrays, and one gas sample inlet pipe, and the second floor was equipped with three bare-bead thermocouple arrays, four bi-directional probe plus solid thermocouple arrays, and one gas sample inlet pipe. The locations of the instrumentation in the West Structure is shown in Fig.~\ref{fig:west_instrumentation}.

The thermocouples in the bare-bead thermocouple arrays were spaced in the same manner as the arrays in the East Structure. The bi-directional probe and thermocouple arrays contained 8 probes with spacing identical to the arrays at the exterior doors of the East Structure. Gas concentrations were pulled through 9.5~mm (0.375~in) diameter stainless steel tubing located 1.2~m (4~ft) above the floor.
\FloatBarrier

@@

\chapter{Channel Lists}

@@

@@

@@

>>>>

\subsection{Layout}
\label{sec:layout}
Dimensioned floor plans of the East and West Structures are presented in Figures~\ref{fig:east_dimensioned_plan}~and~\ref{fig:west_dimensioned_plan}, respectively.

@@

\begin{figure}[!ht]
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/West_Structure_2nd_Floor_Dimensioned_Full}
	\\~\\
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/West_Structure_1st_Floor_Dimensioned_Full}
	\caption[Dimensioned floor plans of the West Structure.]{Dimensioned floor plan of the second floor (top) and first floor (bottom) of the West Structure.}
	\label{fig:west_dimensioned_plan}
\end{figure}

The interior dimensions of each structure were approximately 6.1~m (20~ft) wide, 11~m (36~ft) long, and 2.4~m (8~ft) high. The stairs connecting the two floors of the West Structure started 1.6~m (5.25~ft) off the south wall with a width of 1.2~m (4~ft) off the east wall and a 0.18~m (7.25~in) rise and 0.19~m (7.5~in) rise. The exterior doors of both structures, the stairwell door on the second level of the West Structure, and a square roof vent with side length 1.2~m (4~ft) and a depth of 0.32~m (12.75~in) were opened and closed at certain instances during experiments to change the ventilation patterns within the structures.
\FloatBarrier

@@

\subsection{East Structure}
The East Structure was instrumented with five bare-bead thermocouple arrays, four bi-directional probe plus solid thermocouple arrays, five total heat flux plus radiometer sensor pairs, and two gas sample inlet pipes at the locations shown in Fig.~\ref{fig:east_instrumentation}.

\begin{figure}[!ht]
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/East_Structure_Dimensioned_Instrumentation}
	\caption{Location of instrumentation in the East Structure.}
	\label{fig:east_instrumentation}
\end{figure}
\FloatBarrier

Each bare-bead thermocouple array was composed of eight thermocouples. Three bi-directional probe and solid thermocouple arrays, such as that presented in Fig.~\ref{fig:BDP_arrays}, were centered in each exterior doorway of the structure and contained eight probes. The fourth bi-directional probe plus solid thermocouple array was located at the opening of the roof vent and contained three probes located approximately 0.30~m (1~ft), 0.61~m (2~ft), and 0.91~m (3~ft) off the north wall of the vent and centered between the east and west sides of the vent as pictured in Fig.~\ref{fig:BDP_arrays}. The total heat flux guage/radiometer pairs were set to be aimed to view the ceiling. Gas concentrations were pulled through 9.5~mm (0.375~in) diameter stainless steel tubing. The height of each individual sensor in the sensor arrays are listed in the channel list found in Table~\ref{table:east_channel_list}.

@@

@@

% MEASUREMENT TYPE FOR BDPs = 'Velocity' OR 'Pressure'?

@@

% \midrule

@@

\multirow{3}{*}{\large{\textbf{A10}}}
 & BDP\_A10\_1 & 0.32~m above ceiling & Velocity \\
 & BDP\_A10\_2 & 0.32~m above ceiling & Velocity \\
 & BDP\_A10\_3 & 0.32~m above ceiling & Velocity \\

@@

\subsection{West Structure}
The first floor of the West Structure was instrumented with three bare-bead thermocouple arrays, three bi-directional probe plus solid thermocouple arrays, and one gas sample inlet pipe, and the second floor was equipped with three bare-bead thermocouple arrays, four bi-directional probe plus solid thermocouple arrays, and one gas sample inlet pipe. The locations of the instrumentation in the West Structure is shown in Fig.~\ref{fig:west_instrumentation}.

The thermocouples in the bare-bead thermocouple arrays were spaced in the same manner as the arrays in the East Structure. The bi-directional probe and thermocouple arrays contained 8 probes with spacing identical to the arrays at the exterior doors of the East Structure. Gas concentrations were pulled through 9.5~mm (0.375~in) diameter stainless steel tubing located 1.2~m (4~ft) above the floor.
\clearpage
\caption{West Structure Channel List\label{table:west_channel_list}} \\
\multirow{11}{*}{\large\textbf{A1}} 
\multirow{16}{*}{\large{\textbf{A4}}}
 & TC\_A4\_1  & 0.03~m below soffit  & Temperature \\
 & TC\_A4\_2  & 0.30~m below soffit  & Temperature \\
 & TC\_A4\_3  & 0.61~m below soffit  & Temperature \\
 & TC\_A4\_4  & 0.91~m below soffit  & Temperature \\
 & TC\_A4\_5  & 1.22~m below soffit  & Temperature \\
 & TC\_A4\_6  & 1.52~m below soffit  & Temperature \\
 & TC\_A4\_7  & 1.83~m below soffit  & Temperature \\
 & TC\_A4\_8  & 2.13~m below soffit  & Temperature \\
 & BDP\_A4\_1 & 0.03~m below soffit  & Velocity \\
 & BDP\_A4\_2 & 0.30~m below soffit  & Velocity \\
 & BDP\_A4\_3 & 0.61~m below soffit  & Velocity \\
 & BDP\_A4\_4 & 0.91~m below soffit  & Velocity \\
 & BDP\_A4\_5 & 1.22~m below soffit  & Velocity \\
 & BDP\_A4\_6 & 1.52~m below soffit  & Velocity \\
 & BDP\_A4\_7 & 1.83~m below soffit  & Velocity \\
 & BDP\_A4\_8 & 2.13~m below soffit  & Velocity \\
\multirow{16}{*}{\large{\textbf{A5}}}
 & TC\_A5\_1  & 0.03~m below soffit  & Temperature \\
 & TC\_A5\_2  & 0.30~m below soffit  & Temperature \\
 & TC\_A5\_3  & 0.61~m below soffit  & Temperature \\
 & TC\_A5\_4  & 0.91~m below soffit  & Temperature \\
 & TC\_A5\_5  & 1.22~m below soffit  & Temperature \\
 & TC\_A5\_6  & 1.52~m below soffit  & Temperature \\
 & TC\_A5\_7  & 1.83~m below soffit  & Temperature \\
 & TC\_A5\_8  & 2.13~m below soffit  & Temperature \\
 & BDP\_A5\_1 & 0.03~m below soffit  & Velocity \\
 & BDP\_A5\_2 & 0.30~m below soffit  & Velocity \\
 & BDP\_A5\_3 & 0.61~m below soffit  & Velocity \\
 & BDP\_A5\_4 & 0.91~m below soffit  & Velocity \\
 & BDP\_A5\_5 & 1.22~m below soffit  & Velocity \\
 & BDP\_A5\_6 & 1.52~m below soffit  & Velocity \\
 & BDP\_A5\_7 & 1.83~m below soffit  & Velocity \\
 & BDP\_A5\_8 & 2.13~m below soffit  & Velocity \\
\multirow{16}{*}{\large{\textbf{A6}}}
 & TC\_A6\_1  & 0.03~m below soffit  & Temperature \\
 & TC\_A6\_2  & 0.30~m below soffit  & Temperature \\
 & TC\_A6\_3  & 0.61~m below soffit  & Temperature \\
 & TC\_A6\_4  & 0.91~m below soffit  & Temperature \\
 & TC\_A6\_5  & 1.22~m below soffit  & Temperature \\
 & TC\_A6\_6  & 1.52~m below soffit  & Temperature \\
 & TC\_A6\_7  & 1.83~m below soffit  & Temperature \\
 & TC\_A6\_8  & 2.13~m below soffit  & Temperature \\
 & BDP\_A6\_1 & 0.03~m below soffit  & Velocity \\
 & BDP\_A6\_2 & 0.30~m below soffit  & Velocity \\
 & BDP\_A6\_3 & 0.61~m below soffit  & Velocity \\
 & BDP\_A6\_4 & 0.91~m below soffit  & Velocity \\
 & BDP\_A6\_5 & 1.22~m below soffit  & Velocity \\
 & BDP\_A6\_6 & 1.52~m below soffit  & Velocity \\
 & BDP\_A6\_7 & 1.83~m below soffit  & Velocity \\
 & BDP\_A6\_8 & 2.13~m below soffit  & Velocity \\
\multirow{8}{*}{\large{\textbf{A7}}}
 & TC\_A7\_1  & 0.03~m below ceiling & Temperature \\
 & TC\_A7\_2  & 0.30~m below ceiling & Temperature \\
 & TC\_A7\_3  & 0.61~m below ceiling & Temperature \\
 & TC\_A7\_4  & 0.91~m below ceiling & Temperature \\
 & TC\_A7\_5  & 1.22~m below ceiling & Temperature \\
 & TC\_A7\_6  & 1.52~m below ceiling & Temperature \\
 & TC\_A7\_7  & 1.83~m below ceiling & Temperature \\
 & TC\_A7\_8  & 2.13~m below ceiling & Temperature \\
\multirow{8}{*}{\large{\textbf{A8}}}
 & TC\_A8\_1  & 0.03~m below ceiling & Temperature \\
 & TC\_A8\_2  & 0.30~m below ceiling & Temperature \\
 & TC\_A8\_3  & 0.61~m below ceiling & Temperature \\
 & TC\_A8\_4  & 0.91~m below ceiling & Temperature \\
 & TC\_A8\_5  & 1.22~m below ceiling & Temperature \\
 & TC\_A8\_6  & 1.52~m below ceiling & Temperature \\
 & TC\_A8\_7  & 1.83~m below ceiling & Temperature \\
 & TC\_A8\_8  & 2.13~m below ceiling & Temperature \\
\multirow{8}{*}{\large{\textbf{A9}}}
 & TC\_A9\_1  & 0.03~m below ceiling & Temperature \\
 & TC\_A9\_2  & 0.30~m below ceiling & Temperature \\
 & TC\_A9\_3  & 0.61~m below ceiling & Temperature \\
 & TC\_A9\_4  & 0.91~m below ceiling & Temperature \\
 & TC\_A9\_5  & 1.22~m below ceiling & Temperature \\
 & TC\_A9\_6  & 1.52~m below ceiling & Temperature \\
 & TC\_A9\_7  & 1.83~m below ceiling & Temperature \\
 & TC\_A9\_8  & 2.13~m below ceiling & Temperature \\
\multirow{19}{*}{\large\textbf{A10}} 
 & TC\_A10\_1  & 0.03~m below soffit & Temperature \\
 & TC\_A10\_2  & 0.30~m below soffit & Temperature \\
 & TC\_A10\_3  & 0.61~m below soffit & Temperature \\
 & TC\_A10\_4  & 0.91~m below soffit & Temperature \\
 & TC\_A10\_5  & 1.22~m below soffit & Temperature \\
 & TC\_A10\_6  & 1.52~m below soffit & Temperature \\
 & TC\_A10\_7  & 1.83~m below soffit & Temperature \\
 & TC\_A10\_8  & 2.13~m below soffit & Temperature \\
 & BDP\_A10\_1 & 0.03~m below soffit  & Velocity \\
 & BDP\_A10\_2 & 0.30~m below soffit  & Velocity \\
 & BDP\_A10\_3 & 0.61~m below soffit  & Velocity \\
 & BDP\_A10\_4 & 0.91~m below soffit  & Velocity \\
 & BDP\_A10\_5 & 1.22~m below soffit  & Velocity \\
 & BDP\_A10\_6 & 1.52~m below soffit  & Velocity \\
 & BDP\_A10\_7 & 1.83~m below soffit  & Velocity \\
 & BDP\_A10\_8 & 2.13~m below soffit  & Velocity \\
\multirow{16}{*}{\large{\textbf{A11}}}
 & TC\_A11\_1  & 0.03~m below soffit  & Temperature \\
 & TC\_A11\_2  & 0.30~m below soffit  & Temperature \\
 & TC\_A11\_3  & 0.61~m below soffit  & Temperature \\
 & TC\_A11\_4  & 0.91~m below soffit  & Temperature \\
 & TC\_A11\_5  & 1.22~m below soffit  & Temperature \\
 & TC\_A11\_6  & 1.52~m below soffit  & Temperature \\
 & TC\_A11\_7  & 1.83~m below soffit  & Temperature \\
 & TC\_A11\_8  & 2.13~m below soffit  & Temperature \\
 & BDP\_A11\_1 & 0.03~m below soffit  & Velocity \\
 & BDP\_A11\_2 & 0.30~m below soffit  & Velocity \\
 & BDP\_A11\_3 & 0.61~m below soffit  & Velocity \\
 & BDP\_A11\_4 & 0.91~m below soffit  & Velocity \\
 & BDP\_A11\_5 & 1.22~m below soffit  & Velocity \\
 & BDP\_A11\_6 & 1.52~m below soffit  & Velocity \\
 & BDP\_A11\_7 & 1.83~m below soffit  & Velocity \\
 & BDP\_A11\_8 & 2.13~m below soffit  & Velocity \\
\multirow{16}{*}{\large{\textbf{A13}}}
 & TC\_A13\_1  & 0.03~m below soffit  & Temperature \\
 & TC\_A13\_2  & 0.30~m below soffit  & Temperature \\
 & TC\_A13\_3  & 0.61~m below soffit  & Temperature \\
 & TC\_A13\_4  & 0.91~m below soffit  & Temperature \\
 & TC\_A13\_5  & 1.22~m below soffit  & Temperature \\
 & TC\_A13\_6  & 1.52~m below soffit  & Temperature \\
 & TC\_A13\_7  & 1.83~m below soffit  & Temperature \\
 & TC\_A13\_8  & 2.13~m below soffit  & Temperature \\
 & BDP\_A13\_1 & 0.03~m below soffit  & Velocity \\
 & BDP\_A13\_2 & 0.30~m below soffit  & Velocity \\
 & BDP\_A13\_3 & 0.61~m below soffit  & Velocity \\
 & BDP\_A13\_4 & 0.91~m below soffit  & Velocity \\
 & BDP\_A13\_5 & 1.22~m below soffit  & Velocity \\
 & BDP\_A13\_6 & 1.52~m below soffit  & Velocity \\
 & BDP\_A13\_7 & 1.83~m below soffit  & Velocity \\
 & BDP\_A13\_8 & 2.13~m below soffit  & Velocity \\
\multirow{16}{*}{\large{\textbf{A14}}}
 & TC\_A14\_1  & 0.03~m below soffit  & Temperature \\
 & TC\_A14\_2  & 0.30~m below soffit  & Temperature \\
 & TC\_A14\_3  & 0.61~m below soffit  & Temperature \\
 & TC\_A14\_4  & 0.91~m below soffit  & Temperature \\
 & TC\_A14\_5  & 1.22~m below soffit  & Temperature \\
 & TC\_A14\_6  & 1.52~m below soffit  & Temperature \\
 & TC\_A14\_7  & 1.83~m below soffit  & Temperature \\
 & TC\_A14\_8  & 2.13~m below soffit  & Temperature \\
 & BDP\_A14\_1 & 0.03~m below soffit  & Velocity \\
 & BDP\_A14\_2 & 0.30~m below soffit  & Velocity \\
 & BDP\_A14\_3 & 0.61~m below soffit  & Velocity \\
 & BDP\_A14\_4 & 0.91~m below soffit  & Velocity \\
 & BDP\_A14\_5 & 1.22~m below soffit  & Velocity \\
 & BDP\_A14\_6 & 1.52~m below soffit  & Velocity \\
 & BDP\_A14\_7 & 1.83~m below soffit  & Velocity \\
 & BDP\_A14\_8 & 2.13~m below soffit  & Velocity \\
